---
title: "Factor Congruence coefficient"
author: "Vinita Vader"
output:
  html_document: 
    toc: yes
    toc_float: true
    df_print: paged
    theme: cosmo
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(jtools)
library(readxl)
library(readr)
library(glue)
library(vctrs)
library(fs)
library(kableExtra)
library(DT)
library(rmarkdown)
library(purrr)
library(knitr)

options("digits" = 6)
```


# Functions
##  Data wrangling 
   - data to obtain inputs for congruence coefficient matrices 
```{r}
#Call data = Ipsatized or Original data 
files <- function(dataType){
  dir_ls(here::here("data"))%>%
  as_tibble() %>% 
  filter(str_detect(value, {{dataType}}))
}

#creating the main col names - factor# and dpecify g or ng
rename_df <- function(d) {
  #look for the col which has sum of NA's equal to the number of rows in the data frame - we want to remove this blank col - output is logical
  col_miss_log <- apply(d, 2, function(x) sum(is.na(x)) == nrow(d))
  #Give the col which has logical = T; this is the blank col
  col_miss <- seq_along(d)[col_miss_log]
  #Remove the first col, the blank col and the co next to blank col
  d_subset <- d[ ,-c(1, col_miss, col_miss + 1)]
  #create the main stem for g_
  nms1 <- gsub("^(\\d?\\d).+", "g_\\1", names(d_subset)[seq(1, col_miss - 2)])
  nms2 <- gsub("^(\\d?\\d).+", "ng_\\1", names(d_subset)[seq(col_miss - 1, length(names(d_subset)))])
  names(d_subset) <- c(nms1, nms2)
  d_subset
}

#add sheet name to the factor names = g/ng_sheetname_fact#
add_sheetname <- function(d, sheetname) {
  d <- rename_df(d)
  prefix <- gsub("\\d", "", names(d))
  digits <- gsub("\\D", "", names(d))
  nms <- paste0(prefix, sheetname, "_", digits)
  names(d) <- nms
  d
}


final_data <- function(dataType){
  file <- files({{dataType}})
  sheets <- readxl::excel_sheets(file$value)
  list_sheets <- map(sheets, ~readxl::read_xlsx(file$value, sheet = .x, n_max = 360))

  list_all_sheets <- map2(list_sheets, sheets, add_sheetname)
  list_all_sheets
}
```

## Input for HungarianSolver
```{r}
#splits each list into two dataframes called grads and non-grads
split_list <- function(d){
  #create the "grads" dataframe
  grads <- d %>%
   data.frame() %>% 
    dplyr::select(starts_with('g')) %>% 
    tibble()
  
   #create the "non-grads" dataframe
  nograds <- d %>%
   data.frame() %>% 
    dplyr::select(starts_with('ng')) %>% 
    tibble()

  #build a list of these two dataframes
l <- list(grads, nograds)
names(l) <- c("grads", "nograds")
l #output the list
}


#Get a list of all congruence coefficients 
congrunce_mat_unnamed <- function(dataType){
  
  #get the list of sheets - appropriate var names
  ips.raw_data <- final_data({{dataType}})
  
  #split the lists into grads and non-grads dfs
  list_all <- map(ips.raw_data, split_list)
  
  #get congruence coefficients for each list
 map(list_all, ~psych::factor.congruence(.x$grads, .x$nograds))
}

#Get a list of all congruence coefficients with named matrices 
congrunce_mat <- function(dataType){
  #list of matrices but unnamed
  list_mats <- congrunce_mat_unnamed ({{dataType}})
  
  #get the sheet name to be used for naming the matrices
    file <- files({{dataType}})
  sheet_name <- readxl::excel_sheets(file$value)
  
  #name the dataframes in the list
  names(list_mats) <- c(sheet_name)
  
  #named dataframes in a list of congruence coefficient matrices
  list_mats
}


```

## Matching pairs and melted matrix
```{r}
#Adds id columns to the pairs 
 add_id_pairs <- function(pair){
   df <- pair %>% 
     data.frame() %>% 
     mutate(id = str_c(X1, "_",X2)) %>% 
     rename( "grad" = "X1",
            "no_grad" = "X2" )
   df
 }
 
 #Adds id columns to the mat long 
 add_id_matLong <- function(mat_long){
retain_rows <- mat_long %>%
  data.frame() %>% 
  #extract digits after the 2nd underscore
  mutate(id_g = str_extract(Var1 , "[^_]*$"), 
         id_ng = str_extract(Var2 , "[^_]*$"), 
         id = paste0(id_g, "_", id_ng)) %>% 
  select(-id_g, - id_ng)
retain_rows
 }
 
#Fucntion to compute congruence coefficients
 compute_avg.cc <- function(model){
  avg_cc <- model %>% 
      summarise(avg_cc = mean(abs(cc)))
  avg_cc 
}
```

# Data for Congruence coefficient matrix
 -  columns are renamed 
 -  list of matrices for every sheet 
```{r message=FALSE}
ips_data <- congrunce_mat ("Ipsatized")
orig_data <- congrunce_mat ("Original")
```


```{r}
#In Hungarian $pairs 
# [,1 ] -rownames - "grads"; [,2] - colnames - "non-grads"
RcppHungarian::HungarianSolver(-1*(abs(x)))$pairs

    pairings_ips <- map(ips_data, ~RcppHungarian::HungarianSolver(-1*(abs(.x)))$pairs)#only retain the pairs information 
    pairings_ips <- map(pairings_ips, add_id_pairs)#pairs with id_col
    
    pairings_orig <- map(orig_data, ~RcppHungarian::HungarianSolver(-1*(abs(.x)))$pairs)#only retain the pairs information 
    pairings_orig <- map(pairings_orig, add_id_pairs) #pairs with id_col
```

# Melt matrices
 - melt the congruence coefficient matrices 
 - use an id to retain rows which overlap with the pairs
 - compute average of all absolute values of congruence coefficient for every model 
```{r message=FALSE}
#Figure out how to set decimal places to three in R
# Output of the factors used for the average cc
#Output table for avg. cc's
options(digits=3)
z = congrunce_mat("Ipsatized") 
mat_long_ips <- map(z, ~reshape2::melt(.x, na.rm=TRUE, value.name="cc"))
mat_long_ips <- map(mat_long_ips, add_id_matLong) #mat_long with id_col

r = congrunce_mat("Original") 
mat_long_orig <- map(r, ~reshape2::melt(.x, na.rm=TRUE, value.name="cc"))
mat_long_orig <- map(mat_long_orig, add_id_matLong)#mat_long with id_col
```

# Original Data 

```{r message=FALSE}
#retain the relevant rows in mat_long, they match with the pairings 
final_cc_list_r <- map2(mat_long_orig, pairings_orig, semi_join, by = "id")

all_avg.cc_r <- map(final_cc_list_r,compute_avg.cc) %>% 
               reshape2::melt() %>% 
               select(-variable) %>% 
               rename("Model" = "L1", 
                      "Avg_cc" = "value") %>% 
               select(Model, Avg_cc) %>% 
               mutate(Avg_cc = round(Avg_cc,2))
```


## Original - Pairings
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results='asis')

data.frame() %>%
  DT::datatable() %>%
  knitr::knit_print() %>%
  attr('knit_meta') %>%
  knitr::knit_meta_add() %>%
  invisible()
```

```{r, results='asis'}
map(final_cc_list_r, ~DT::datatable(.x,  options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>%
      htmltools::tagList() %>%
      print())
```

## Original - Average congruence Coefficients 
```{r}
 DT::datatable(all_avg.cc_r, options = list(columnDefs = list(list(className = 'dt-center')))) 
```

# Ipsatized Data 
```{r message=FALSE}
#retain the relevant rows in mat_long, they match with the pairings 
final_cc_list_z <- map2(mat_long_ips, pairings_ips, semi_join, by = "id")

all_avg.cc_z <- map(final_cc_list_z,compute_avg.cc) %>% 
               reshape2::melt() %>% 
               select(-variable) %>% 
               rename("Model" = "L1", 
                      "Avg_cc" = "value") %>% 
               select(Model, Avg_cc) %>% 
               mutate(Avg_cc = round(Avg_cc,2))
```

## Ipsatized - Pairings  
```{r, results='asis'}
map(final_cc_list_z, ~DT::datatable(.x, options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>% 
      htmltools::tagList() %>%
      print())
```

## Ipsatized - Average congruence Coefficients 
```{r}
 DT::datatable(all_avg.cc_z, options = list(columnDefs = list(list(className = 'dt-center')))) 
```


```{r echo=FALSE, eval=FALSE}
#Write in excel sheet to send 
filename <- "/Users/vinitavader/Desktop/EVERYTHING/Persian_High Dimensionality/scripts/models_cc.xlsx"

rio::export(list(Orig_models = all_avg.cc_r, Ips_models = all_avg.cc_r), filename)
```

